---
title: "WU_LMP"
author: "Jaci Heckman"
date: "Summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)
```

## Regression Model One

```{r}
model1 <- lm(SIMS~ARM, data=data)
plot(SIMS~ARM, data=data)
abline(model1)
summary.lm(model1)
title(main="Plot of SIMS versus ARM")
```


## Predictions

```{r}
new <- data.frame(ARM=88, GRIP=94)
```

```{r}
predict(model1,new,interval="prediction")
```
  
## Regression Model Two

```{r}
model2 <- lm(SIMS~GRIP, data=data)
plot(SIMS~GRIP, data=data)
abline(model2)
summary.lm(model2)
title(main="Plot of SIMS versus GRIP")
```


## Predictions

```{r}
new <- data.frame(ARM=88, GRIP=94)
```

```{r}
predict(model2,new,interval="prediction")
```

## Regression Model Three

```{r}
model3 <- lm(SIMS~ARM+GRIP, data=data)
plot(SIMS~ARM+GRIP, data=data)
abline(model3)
summary.lm(model3)
title(main="Plot of SIMS versus GRIP and ARM")
```

## Predictions

```{r}
new <- data.frame(ARM=88, GRIP=94)
```

```{r}
predict(model3,new,interval="prediction")
```



## Model Comparison Using Anova
  
Comparing Model 1 to Model 3
```{r}
anova(model1, model3)
```
  
Comparing Model 2 to Model 3  
```{r}
anova(model2, model3)
```

Informal Comparison
Comparing model 1 to model 2
```{r}
anova(model1, model2)
```


## Inferential Data

```{r}
model1 <- aov(SIMS~ARM+GRIP,data=data)
summary.aov(model1)
```

## Discussion and Conclusion

  The analysis of each Anova comparison shows us differences in SIMS when it is graphed and displayed. In our first comparison model, the RSS differences of model1 is 217, model 3 has 188. In our second, the RSS difference of model 1 is now 243, model2 is now 188. In the informal comparison, the comparison RSS is 188 for model 1 and 243 for model 2. 
  
  This data is tied to our original models 1 through 3. The "Model" in each comparison represents the listed model data that was previously plotted. This data shows us that GRIP is not favored when compared to ARM. The p-value is telling of this information, .000000000000002, this number is almost non-existent suggesting a small inference. 

